---
title: "Covariate: Add Dummy | Polynomial, Rm Near Zero"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup

```{r}
library(caret)
library(ISLR)
data(Wage)
```

```{r}
inTrain <- createDataPartition(y = Wage$wage, p = 0.7, list = FALSE)
training <- Wage[inTrain,]
testing <- Wage[-inTrain,]
```

## Common covariates to add dummy variables

Basic idea is to convert factor variables to indicator variables

```{r}
table(training$jobclass)
```

```{r}
dummies <- dummyVars(wage ~ jobclass, data = training)
head(predict(dummies, newdata = training))
```

## Removing near zero covariates

Removing less meaningful predictors who should not be used in a prediction model

```{r}
nsv <- nearZeroVar(training, saveMetrics = TRUE)
nsv
```

## Spline Basis

### Creating a polynomial model

```{r}
library(splines)
bsBasis <- bs(training$age, df = 3)
head(bsBasis)
```

### Fitting model to train set

```{r}
lm1 <- lm(wage ~ bsBasis, data = training)
plot(training$age, training$wage, pch = 19, cex = 0.5)
points(training$age, predict(lm1, newdata = training), col = "red", pch = 19, cex = 0.5)
```

### Fitting model to test set

```{r}
aux <- predict(bsBasis, age = testing$age)
head(aux)
```

Key search in Google: feature extraction for [data type]